Nanophotonic Computational Design

### 2013-02-22 defense/pres2.tex
Added fib pics.
Added 3D pictures.

\oursection{Direct design with regularization}
\I  Direct design ``works'' but not practical
    \BE \minimize_z \|A(z)x - b\|^2 \EE
\I  So, let's add a \emph{regularization} term to $z$ and solve the following instead 
    \BE \minimize_z \|A(z)x - b\|^2 + \eta\|z-z_0\|^2 \EE
    \BI  $\|z-z_0\|^2$ term keeps $z$ close to $z_0$
    \I  $\eta$ controls the strength of the regularization \EI
\I  Solution can still be computed in one step
\nextpage

@@

\oursection{Iterative design of nanophotonic devices}
\I  New algorithm: Iteratively solve for $x$ (field) and $z$ (structure)
    \begin{align*} 
    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2 \\
    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2 
    \end{align*}
\I  Takes advantage of the \emph{bi-linearity} of the physics residual
    \BI Jointly solving for $x$ and $z$ is a non-convex problem \EI
\nextpage

@@

\oursection{Iterative design with hard constraints on $z$}
\I  We can also put hard limits on $z$ (structure)
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2\\
    \subto & z_\text{min} \le z \le z_\text{max}
    \end{align*}
\I  $z_\text{min} \le z \le z_\text{max}$ constraint 
    better represents manufacturability constraint
    \BI Corresponds to a minimum and maximum allowable permittivity ($\epsilon$) \EI
\nextpage

@@

\oursection{Objective-first design of linear devices}
\I  Next realization: for linear components, 
    only certain elements of $x$ (field) matter
    \BI Specifically, the elements of $x$ at the input/output ports \EI
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 \\
    \subto & x_\text{boundary} - \hat{x}_\text{boundary} = 0 \\
        & z_\text{min} \le z \le z_\text{max}
    \end{align*}
\I  Instead of regularization term, we force the elements of $x$
    at the boundary to be equal to the ideal case ($\hat{x}$)
\nextpage

@@

\I  Scalable
    \BI Far outstrips computing clusters such as Teragrid
    \I  Can perform multiple solves in parallel, on a single Matlab instance 
    \I  All computation is performed externally (in the cloud) \EI

\I  Easy to use
    \BI Installs with a single Matlab command
    \I  Solves completed with a single Matlab command: \verb+maxwell(...);+ \EI

\I  The key technological enabler in achieving 3D design
\nextpage

\oursection{3D design: problem statement}
\begin{align*}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align*}
\I  $M$ modes with $N_i$ monitored output modes each
    \BI $b_i$ is the input excitation for each mode
    \I  $|c_{ij}\T x_i|$ is the field overlap with output mode $c_{ij}$
    \I  $\alpha_{ij}$ and $\beta_{ij}$ is the design range for the overlap \EI
\nextpage

\I  Show input and output modes here as explanation of problem statement
\I  Use 3D model of wgc_te as example.
\nextpage

\EI
\end{document}

>>>>

\oursection{Direct design with regularization}
\stepwise{
\I  Direct design ``works'' but not practical
    \BE \minimize_z \|A(z)x - b\|^2 \EE
\step{\I  So, let's add a \emph{regularization} term to $z$ and solve the following instead 
    \BE \minimize_z \|A(z)x - b\|^2 + \eta\|z-z_0\|^2 \EE}
    \step{\BI  $\|z-z_0\|^2$ term keeps $z$ close to $z_0$
    \I  $\eta$ controls the strength of the regularization \EI

\I  Solution can still be computed in one step}
}
\nextpage

@@

\oursection{Iterative design of nanophotonic devices}
\I  New algorithm: Iteratively solve for $x$ (field) and $z$ (structure)
    \pause
    \begin{align*} 
    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2 \\
    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2 
    \end{align*}
    \pause
\I  Takes advantage of the \emph{bi-linearity} of the physics residual
    \BI Jointly solving for $x$ and $z$ is a non-convex problem \EI
\nextpage

@@

\oursection{Iterative design with hard constraints on $z$}
\I  We can also put hard limits on $z$ (structure)
    \pause
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2\\
    \subto & z_\text{min} \le z \le z_\text{max}
    \end{align*}
    \pause
\I  $z_\text{min} \le z \le z_\text{max}$ constraint 
    better represents manufacturability constraint
    \BI Corresponds to a minimum and maximum allowable permittivity ($\epsilon$) \EI
\nextpage

@@

\oursection{Objective-first design of linear devices}
\stepwise{
\I  Next realization: for linear components, 
    only certain elements of $x$ (field) matter
\step{\BI Specifically, the elements of $x$ at the input/output ports \EI}
\step{
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 \\
    \subto & x_\text{boundary} - \hat{x}_\text{boundary} = 0 \\
        & z_\text{min} \le z \le z_\text{max}
    \end{align*}
}
\step{
\I  Instead of regularization term, we force the elements of $x$
    at the boundary to be equal to the ideal case ($\hat{x}$)}
}
\nextpage

@@

\I  Scalable
    \BI Far outstrips computing clusters such as Teragrid
    \I  Can perform multiple solves in parallel, on a single Matlab instance 
    \I  All computation is performed externally (in the cloud) \EI
\pause
\I  Easy to use
    \BI Installs with a single Matlab command
    \I  Solves completed with a single Matlab command: \verb+maxwell(...);+ \EI
\pause
\I  The key technological enabler in achieving 3D design
\nextpage

\oursection{3D design: problem statement}
\stepwise{
    \step{
\begin{align*}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align*}
    }
\step{
\I  $M$ modes with $N_i$ monitored output modes each}
    \step{\BI $b_i$ is the input excitation for each mode
    \I  $|c_{ij}\T x_i|$ is the field overlap with output mode $c_{ij}$
    \I  $\alpha_{ij}$ and $\beta_{ij}$ is the design range for the overlap \EI}
}
\nextpage

\medfig{3D_wgc_te}
\I  Input mode is excited using current source ($b_i$ or $-i\omega J$)
\I  Output mode is enforced using overlap integrals
    ($c_{ij}\T x_i$ or $\int \hat{E_{ij}} E$)
\nextpage

% \oursection{Structure of 3D designs}
% \I  250 nm silicon slab surrounded by silica

\I TE mode converter
\smallfig{takeaway}
\I  Efficiency: 86.4\%
\I  Power in rejection mode (transmitted fundamental): 0.7\%
\I  250 nm silicon slab surrounded by silica
\newpage

\medfig{3D_wgc_tm}
\nextpage

\I TM mode converter
\smallfig{wgc_tm}
\I  Efficiency: 76.9\%
\I  Power in rejection mode (transmitted fundamental): 1.0\%
\newpage

\medfig{3D_spl_modal}
\nextpage

\I  Spatial mode splitter
\BI  Efficiency: 88.7\%, 77.4\% (0.27\%, 0.20\%) \EI
\medfig{spl_modal}
\newpage

\medfig{3D_spl_tetm}
\nextpage

\I  TE/TM splitter
\BI  Efficiency: 87.6\%, 88.8\% (1.06\%, 0.58\%) \EI
\medfig{spl_tetm}
\newpage

\medfig{3D_spl_wdm}
\nextpage

\I  Wavelength splitter
\BI  Efficiency: 83.2\%, 78.7\% (0.49\%, 1.66\%) \EI
\medfig{spl_wdm}
\newpage

\medfig{3D_hub_3x3}
\nextpage

\I 3x3 hub (88.6\%, 90.6\%, 87.3\% efficiency)
\bigfig{hub_3x3}
\newpage

\medfig{3D_hub_4x4}
\nextpage

\I 4x4 hub
\bigfig{hub_4x4_eps}
\newpage

\I Efficiency: 85.9\%, 88.1\%, 85.4\%, 84.3\%
\bigfig{hub_4x4}
\newpage

\medfig{3D_hub_2x2x2}
\nextpage

\I 2x2x2 hub (77.6\%, 73.7\%, 75.7\%, 75.2\% efficiency)
\bigfig{hub_2x2x2}
\newpage

\medfig{3D_fib_te}
\nextpage

\I fiber coupler (51.5\%)
\medfig{fib_te}
\newpage

\medfig{3D_fib_pol}
\nextpage

\I fiber coupler mode splitter (32.6\%, 22.7\%)
\bigfig{fib_pol}
\newpage

\medfig{3D_fib_wdm}
\nextpage

\I fiber coupler wdm (31.6\%, 28.6\%)
\bigfig{fib_wdm}
\newpage
\EI
\end{document}
